Asian Biased Hate Crime Trends in Toronto

### 2024-09-28 paper/paper.qmd
proper cross referencing

The following structure of this paper is as follows: Section @sec-mydatasection presents the data sources and methodology, followed by Section 3, which discusses the results and their implications. Section 4 concludes with a discussion of the limitations of the study and suggestions for future research.

@@

The columns included in the analysis are Primary Offences (Regrouped), Race Bias and Occurance Year. Due to the analysis’ focus on Asian Bias hate crimes, races of only East, Southeast and South Asian descent were included. Furthermore, primary offences were regrouped into more general overarching categories including, Assault-Related, Threats and Harassment, Mischief & Property Damage, Hate-Related and Others. Only the occurrence year was included as opposed to full dates, and reported dates were used to focus on high-level trends. Additionally, the dataset did not contain information on other socio-economic factors related to location, such as mean income levels and ethnic demographics, thus locations were excluded. Furthermore, location type was recategorized into more general categories including public, private, government, casual and other places.

# Results

@@

# Discussion

@@

# Limitations and Next Steps

>>>>

The following structure of this paper is as follows:  @sec-mydatasection presents the data sources and methodology, then  @sec-myresults followed by  @sec-mydisc, which discusses the results and their implications.  @sec-mylimits concludes with a discussion of the limitations of the study and suggestions for future research.

@@

The columns included in the analysis are Primary Offences (Regrouped), Race Bias and Occurence Year. Due to the analysis’ focus on Asian Bias hate crimes, races of only East, Southeast and South Asian descent were included. Furthermore, primary offences were regrouped into more general overarching categories including, Assault-Related, Threats and Harassment, Mischief & Property Damage, Hate-Related and Others. Only the occurrence year was included as opposed to full dates, and reported dates were used to focus on high-level trends. Additionally, the dataset did not contain information on other socio-economic factors related to location, such as mean income levels and ethnic demographics, thus locations were excluded. Furthermore, location type was recategorized into more general categories including public, private, government, casual and other places.

# Results {#sec-myresults}

@@

# Discussion {#sec-mydisc}

@@

# Limitations and Next Steps {#sec-mylimits}
